Report and Figures

### 2016-12-15 figs.Rmd
added rounding to max info

cache %>% 
  filter(city %in% c('Atlanta', 'Philadelphia')) %>% 
  select(city, I_XY) %>% 
  spread(key = city, value = I_XY, fill = NA) %>% 
  write_csv('figs/max_information.csv')

>>>>

cache %>% 
  filter(city %in% c('Atlanta', 'Philadelphia')) %>% 
  select(city, I_XY) %>% 
  mutate(I_XY = round(I_XY,2)) %>% 
  spread(key = city, value = I_XY, fill = NA) %>% 
  write_csv('figs/max_information.csv')
